---
title: "Lab 10: Interactive visualization"
author: "Zejian Huang"
date: "11/25/2018"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  html_document:
    highlight: tango
    self_contained: true
  pdf_document:
    highlight: tango
  github_document:
    html_preview: false
---

```{r setup, include = FALSE}
# DO NOT ALTER CODE IN THIS CHUNK
# Set knitr options
knitr::opts_chunk$set(
  echo = TRUE, eval = TRUE, fig.width = 5,
  fig.asp = 0.618, out.width = "80%", dpi = 120,
  fig.align = "center", cache = FALSE
)

# Load packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(highcharter))
suppressPackageStartupMessages(library(leaflet))

# Load dataset
mtcars <- read.csv("Cars.csv")
school <- read.csv("School_University_100.csv")
```

---

## Exercise 1
```{r}
hchart(mtcars, "scatter", hcaes(x = hp, y = mpg, group = cyl)) %>%   
  hc_title(text = "Miles per gallon vs Gross horsepower") %>%   
  hc_xAxis(title = list(text = "Gross horsepower")) %>%   
  hc_yAxis(title = list(text = "Miles per gallon")) 
```
The trend in the plot shows that MPG is decreasing when gross horsepower increases and number of cylinders increases. 

## Exercise 2
```{R}
hchart(mtcars, type = "bar", hcaes(x = Name, y = hp, group = carb)) %>%   
  hc_title(text = "Gross horsepower and number of carburetors by car") %>%   
  hc_xAxis(title = list(text = "Car")) %>%   
  hc_yAxis(title = list(text = "Gross horsepower")) %>%   
  hc_add_theme(hc_theme_elementary())
```
1: hornet 4 drive,
2: hornet sportabout and pontiac firebird,
3: Merc 450SL, Merc 450SE, Merc 450SLC,
4: Ford Pantera L,
6: Ferrari Dino, 
8: Maserati Bora. 

## Exercise 3
```{r}
leaflet() %>%   
  addProviderTiles(providers$Esri.NatGeoWorldMap) %>%   
  setView(lng = -73.94731, lat = 40.69673, zoom = 10)
```
When we increase zoom, the map is more accurate and detailed. When we decrease zoom, the map is more brief and covered places are more than higher zoom.  


## Exercise 4
```{r}
leaflet() %>%   
  addTiles() %>%   
  setView(lng = -100.243683, lat =  34.052235, zoom = 3) %>%   
  addMarkers(lat = school$lat, lng = school$lon)
```

```{r}
leaflet() %>%   
  addTiles() %>%   
  setView(lng = -100.243683, lat =  34.052235, zoom = 3) %>%   
  addCircleMarkers(lat = school$lat, lng = school$lon)
```

```{r}
leaflet() %>%   
  addTiles() %>%   
  setView(lng = -100.243683, lat =  34.052235, zoom = 3) %>%   
  addMarkers(lat = school$lat, lng = school$lon,              
             popup = paste("School name:", school$School_Name, "<br>",                            "School rank:", school$School_Rank))
```

## Exercise 5
```{r}
leaflet() %>%   
  addTiles() %>%   
  setView(lng = -100.243683, lat =  34.052235, zoom = 3) %>%   
  addMarkers(lat = school$lat, lng = school$lon,              
             popup = paste("School name:", school$School_Name, "<br>",                                                    "School rank:", school$School_Rank, 
                           "School URL:", school$School_Url))
```


